---
output:
  html_document: default
  pdf_document: default
---
```{r}
library(quantmod)
library(PerformanceAnalytics)
library(xts)
```
## load data 
```{r}
data.AMD<-getSymbols("AMD", from ="2013-12-31",to="2017-10-31",auto.assign = FALSE)
data.SOXL <-getSymbols("SOXL",from ="2013-12-31", to="2017-10-31",auto.assign = FALSE)
data.FAF <-getSymbols("FAF", from ="2013-12-31", to="2017-10-31",auto.assign = FALSE)
```


##CPR
```{r}
#return.SOXL <- Return.calculate(data.SOXL$SOXL.Adjusted)
#Return.cumulative(return.SOXL)
return.AMD <- Return.calculate(data.AMD$AMD.Adjusted)
return.SOXL <- Return.calculate(data.SOXL$SOXL.Adjusted)
return.FAF <- Return.calculate(data.FAF$FAF.Adjusted)


multi <-cbind(return.AMD, return.SOXL, return.FAF)
multi <- multi[-1,]
tail(multi)
#Return.cumulative(Return.portfolio(multi, weights = c(1/3, 1/3,1/3), rebalance_on = "months"))

Return.cumulative(return.AMD)
Return.cumulative(return.SOXL)
Return.cumulative(return.FAF)
```
##annualized standard deviation
```{r}
mat.return <- matrix(multi, nrow = nrow(multi))
colnames(mat.return) <- c("AMD", "SOXL","FAF")
weight <- c(1/3, 1/3,1/3)
mat.wgt <- matrix(weight,1)
tmat.wgt <- t(mat.wgt)

VCOV <- cov(mat.return) * 252
port.var <-mat.wgt %*% VCOV %*% tmat.wgt
port.var
port.sd <- sqrt(port.var)
port.sd

```
#Risk
##Parkinson Volatility
```{r}
parkinson <- data.SOXL[,c("SOXL.High","SOXL.Low")]
parkinson$log.hi.low<-log(parkinson$SOXL.High/parkinson$SOXL.Low)
parkinson$log.square<-(parkinson$log.hi.low)**2
parkinson.sum<-sum(parkinson$log.square)
parkinson.vol<-sqrt(1/(4*nrow(parkinson)*log(2))*parkinson.sum)
annual.parkinson.vol<-parkinson.vol*sqrt(252)
annual.parkinson.vol
```
##Garman-Klass
```{r}
garman.klass <- data.SOXL[,c("SOXL.Open","SOXL.High","SOXL.Low","SOXL.Close")]
head(garman.klass)
garman.klass.one<- (1/(2*nrow(garman.klass)))*sum((log(garman.klass$SOXL.High/garman.klass$SOXL.Low))**2)
garman.klass.two <-((2*log(2)-1)/nrow(garman.klass)) *sum(log(garman.klass$SOXL.Close/garman.klass$SOXL.Open)**2)
garman.klass.vol<-sqrt(garman.klass.one-garman.klass.two)
annual.garman.klass.vol<-garman.klass.vol*sqrt(252)
annual.garman.klass.vol
```
##Rogers, Satchell, and Yoon
```{r}
rsy.sat.yoon <- data.SOXL[,c("SOXL.Open","SOXL.High","SOXL.Low","SOXL.Close")]
rsy.one<-log(rsy.sat.yoon$SOXL.High/rsy.sat.yoon$SOXL.Close)
rsy.two<-log(rsy.sat.yoon$SOXL.High/rsy.sat.yoon$SOXL.Open)
rsy.one.two<-rsy.one*rsy.two
rsy.three<-log(rsy.sat.yoon$SOXL.Low/rsy.sat.yoon$SOXL.Close)
rsy.four<-log(rsy.sat.yoon$SOXL.Low/rsy.sat.yoon$SOXL.Open)
rsy.three.four<-rsy.three*rsy.four
rsy.vol<-sqrt((1/nrow(rsy.sat.yoon))*sum((rsy.one.two+rsy.three.four)))
annual.rsy.vol<-rsy.vol*sqrt(252)
annual.rsy.vol
```

##Historical VaR 01
```{r}
returns <- cbind(return.AMD, return.SOXL, return.FAF)
returns <- returns[-1,]
names(returns) <- c("AMD.ret","SOXL.ret","FAF.ret")
ret.cum.AMD <- Return.cumulative(returns$AMD.ret)
ret.cum.SOXL <- Return.cumulative(returns$SOXL.ret)
ret.cum.FAF <- Return.cumulative(returns$FAF.ret)
AMD.val <- 1/3 * ( 1 + ret.cum.AMD)
SOXL.val <- 1/3 * ( 1 + ret.cum.SOXL)
FAF.val <- 1/3 * ( 1 + ret.cum.FAF)
last.idx <- c(AMD.val,SOXL.val,FAF.val)
sum(last.idx)
sim.portPnL <- last.idx[1] * returns$AMD.ret+ last.idx[2] * returns$SOXL.ret+last.idx[3] * returns$FAF.ret 
names(sim.portPnL) <- "Port.PnL"
VaR01.Historical=quantile(-sim.portPnL$Port.PnL,0.99)
VaR01.Historical
VaR05.Historical=quantile(-sim.portPnL$Port.PnL,0.95)
VaR05.Historical
```

##Historical Excess Shortfall
```{r}
ES.PnL <-sim.portPnL$Port.PnL
ES.PnL$dummy01<-ifelse(ES.PnL$Port.PnL< (- VaR01.Historical) ,1,0)
ES.PnL$dummy05<-ifelse(ES.PnL$Port.PnL< (-VaR05.Historical) ,1,0)
shortfall01<-subset(ES.PnL,ES.PnL$dummy01==1)
shortfall05<-subset(ES.PnL,ES.PnL$dummy05==1)
ES01.Historical<- -mean(shortfall01$Port.PnL)
ES01.Historical
ES05.Historical<- -mean(shortfall05$Port.PnL)
ES05.Historical
```
##CAPM
```{R}

data.AMD<- to.monthly(data.AMD)
data.SOXL <- to.monthly(data.SOXL)
data.FAF <- to.monthly(data.FAF)

mkt.ret.AMD <- Return.calculate(data.AMD$data.AMD.Adjusted)
mkt.ret.SOXL <- Return.calculate(data.SOXL$data.SOXL.Adjusted)
mkt.ret.FAF <- Return.calculate(data.FAF$data.FAF.Adjusted)

mkt.ret <- cbind(mkt.ret.AMD,mkt.ret.SOXL,mkt.ret.FAF)
mkt.ret <- mkt.ret[-1,]
port.ret<-Return.portfolio(mkt.ret,c(1/3,1/3,1/3),rebalance_on = 'month')

setwd("~/Documents/termC/BUDT758I FIS")

rf <- read.csv("DGS3MO.csv")
rf$date<-as.Date(rf$DATE,"%Y-%m-%d")
rf$DGS3MO<-as.numeric(as.character(rf$DGS3MO))

data.GSPC <- getSymbols("^GSPC", from = "2013-12-31", to = "2017-10-31", auto.assign = FALSE)
data.GSPC <- to.monthly(data.GSPC)
mkt.ret.GSPC <- Return.calculate(data.GSPC$data.GSPC.Adjusted)
mkt.ret.GSPC <- mkt.ret.GSPC[-1,]

#Load	Risk Free	return
rf$DATE <- NULL
rf<-xts(rf$DGS3MO,order.by=rf$date)
names(rf)<-paste("DGS3MO")
rf.monthly<-to.monthly(rf)
rf.monthly<-(1+rf.monthly[,1]/100)^(3/12)-1
rf.sub<-subset(rf.monthly,index(rf.monthly) >= as.yearmon("Jan 2014") & 
                 index(rf.monthly) <= as.yearmon("Oct 2017"))

combo <- cbind(mkt.ret.GSPC$data.GSPC.Adjusted,rf.sub$rf.Open,  port.ret$portfolio.returns)
names(combo)<-paste(c("mkt.ret.GSPC","rf","port.ret"))
head(combo)
#Calculate	excess	portfolio	and	market	return
combo$exret<-combo$port.ret - combo$rf
combo$exmkt<-combo$mkt.ret.GSPC - combo$rf

#Run Regression	of	Excess	Firm	Return	on	Excess	Market	Return
CAPM<-lm(exret~exmkt, data = combo)
summary(CAPM)

```
#Market index prediction 
```{r}
set.seed(987654321)
w1 <- rnorm(100000) # standard normal, mean=0, variance = 1
head(w1,10)
gbm.paths <- function(w1,S0,drift,sigma,dt){
  ST <- S0*exp(drift*dt + sigma*w1*sqrt(dt))
  ST
}

S0 = 2572.83
riskfree=0.0115
sigma = 0.1018 
drift = (riskfree-0.5*sigma^2)
T=0.25
ST <- gbm.paths(w1[1:10000],S0,drift,sigma,T)
stockindexreturnList<-(ST-S0)/S0
stockindexreturn<-mean((ST-S0)/S0)
stockindexrisk<-sd((ST-S0)/S0)
stockindexreturn
stockindexrisk
```


##MV optimization
```{r}
VCOV.MV <- cov(mat.return)
mat.ret<-matrix(mkt.ret,nrow(mkt.ret))
colnames(mat.ret)<-c("AMD.Ret","SOXL.Ret","FAF.Ret")

avg.ret<-matrix(apply(mat.ret,2,mean))
colnames(avg.ret)<-paste("Avg.Ret")
rownames(avg.ret)<-paste(c("AMD", "SOXL","FAF"))

min.ret<-min(avg.ret)
max.ret<-max(avg.ret)

increments=100
tgt.ret<-seq(min.ret,max.ret,length=increments)
head(tgt.ret)
tgt.sd<-rep(0,length=increments)
wgt<-matrix(0,nrow=increments,ncol=length(avg.ret))

library(quadprog)
for (i  in 1:100){
  Dmat<-2*VCOV.MV
  dvec<-c(rep(0,length(avg.ret)))
  Amat<-cbind(rep(1,length(avg.ret)),avg.ret,diag(1,nrow=ncol(mkt.ret)))
  bvec<-c(1,tgt.ret[i],rep(0,ncol(mkt.ret)))
  soln<-solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=2)
  tgt.sd[i]<-sqrt(soln$value)
  wgt[i,]<-soln$solution
}

colnames(wgt)<-paste(c("wgt.AMD", "wgt.SOXL", "wgt.FAF"))
wgt[1,2]<-0
wgt[nrow(wgt),1]<-0

tgt.port<-data.frame(cbind(tgt.ret,tgt.sd,wgt))
minvar.port<-subset(tgt.port,tgt.port$tgt.sd==min(tgt.port$tgt.sd))
riskfree <- 0.0115
tgt.port$Sharpe<-(tgt.port$tgt.ret-riskfree)/tgt.port$tgt.sd
tangency.port<-subset(tgt.port,tgt.port$Sharpe==max(tgt.port$Sharpe))
eff.frontier<-subset(tgt.port,tgt.port$tgt.ret>=minvar.port$tgt.ret)

plot(x=tgt.sd, xlab="Portfolio Risk", y=tgt.ret, ylab="Portfolio Return", col="gray40",
main="Mean-Variance Efficient Frontier")
abline(h=0,lty=1)
points(x=minvar.port$tgt.sd,y=minvar.port$tgt.ret,pch=17,cex=3)
points(x=tangency.port$tgt.sd,y=tangency.port$tgt.ret,pch=19,cex=3)
points(x=eff.frontier$tgt.sd,y=eff.frontier$tgt.ret, col ="pink" )

```

#Recalculate weight#############
##CAPM
```{r}
colnames(mat.return) <- c("AMD", "SOXL","FAF")
weight2 <- c(tangency.port$wgt.AMD,tangency.port$wgt.SOXL,tangency.port$wgt.FAF)
mat.wgt2 <- matrix(weight2,1)
tmat.wgt2 <- t(mat.wgt2)

port.ret2<-Return.portfolio(mkt.ret,weight2,rebalance_on = 'month')

combo2 <- cbind(mkt.ret.GSPC$data.GSPC.Adjusted,rf.sub$rf.Open,port.ret2$portfolio.returns)
names(combo2)<-paste(c("mkt.ret.GSPC","rf","port.ret2"))
head(combo2)

#Calculate	excess	portfolio	and	market	return
combo2$exret2<-combo$port.ret2 - combo$rf
combo2$exmkt<-combo$mkt.ret.GSPC - combo$rf
#Run Regression	of	Excess	Firm	Return	on	Excess	Market	Return
CAPM2<-lm(exret2~exmkt, data = combo2)
summary(CAPM2)
```
##annualized standard deviation
```{r}
mat.return <- matrix(multi, nrow = nrow(multi))
colnames(mat.return) <- c("AMD", "SOXL","FAF")
mat.wgt2 <- matrix(weight2,1)
tmat.wgt2 <- t(mat.wgt2)

VCOV <- cov(mat.return) * 252
port.var <-mat.wgt %*% VCOV %*% tmat.wgt
port.var
port.sd <- sqrt(port.var)
port.sd
```
#Risk
##Parkinson Volatility
```{r}
data.SOXL <-getSymbols("SOXL",from ="2013-12-31", to="2017-10-31",auto.assign = FALSE)
parkinson <- data.SOXL[,c("SOXL.High","SOXL.Low")]
parkinson$log.hi.low<-log(parkinson$SOXL.High/parkinson$SOXL.Low)
parkinson$log.square<-(parkinson$log.hi.low)**2
parkinson.sum<-sum(parkinson$log.square)
parkinson.vol<-sqrt(1/(4*nrow(parkinson)*log(2))*parkinson.sum)
annual.parkinson.vol<-parkinson.vol*sqrt(252)
annual.parkinson.vol
```
##Garman-Klass
```{r}
garman.klass <- data.SOXL[,c("SOXL.Open","SOXL.High","SOXL.Low","SOXL.Close")]
head(garman.klass)
garman.klass.one<- (1/(2*nrow(garman.klass)))*sum((log(garman.klass$SOXL.High/garman.klass$SOXL.Low))**2)
garman.klass.two <-((2*log(2)-1)/nrow(garman.klass)) *sum(log(garman.klass$SOXL.Close/garman.klass$SOXL.Open)**2)
garman.klass.vol<-sqrt(garman.klass.one-garman.klass.two)
annual.garman.klass.vol<-garman.klass.vol*sqrt(252)
annual.garman.klass.vol
```
##Rogers, Satchell, and Yoon
```{r}
rsy.sat.yoon <- data.SOXL[,c("SOXL.Open","SOXL.High","SOXL.Low","SOXL.Close")]
rsy.one<-log(rsy.sat.yoon$SOXL.High/rsy.sat.yoon$SOXL.Close)
rsy.two<-log(rsy.sat.yoon$SOXL.High/rsy.sat.yoon$SOXL.Open)
rsy.one.two<-rsy.one*rsy.two
rsy.three<-log(rsy.sat.yoon$SOXL.Low/rsy.sat.yoon$SOXL.Close)
rsy.four<-log(rsy.sat.yoon$SOXL.Low/rsy.sat.yoon$SOXL.Open)
rsy.three.four<-rsy.three*rsy.four
rsy.vol<-sqrt((1/nrow(rsy.sat.yoon))*sum((rsy.one.two+rsy.three.four)))
annual.rsy.vol<-rsy.vol*sqrt(252)
annual.rsy.vol
```

##Historical VaR 01
```{r}
returns <- cbind(return.AMD, return.SOXL, return.FAF)
returns <- returns[-1,]
names(returns) <- c("AMD.ret","SOXL.ret","FAF.ret")
ret.cum.AMD <- Return.cumulative(returns$AMD.ret)
ret.cum.SOXL <- Return.cumulative(returns$SOXL.ret)
ret.cum.FAF <- Return.cumulative(returns$FAF.ret)
AMD.val <-tangency.port$wgt.AMD * ( 1 + ret.cum.AMD)
SOXL.val <- tangency.port$wgt.SOXL * ( 1 + ret.cum.SOXL)
FAF.val <- tangency.port$wgt.FAF* ( 1 + ret.cum.FAF)
last.idx <- c(AMD.val,SOXL.val,FAF.val)
sum(last.idx)
sim.portPnL <- last.idx[1] * returns$AMD.ret+ last.idx[2] * returns$SOXL.ret+last.idx[3] * returns$FAF.ret 
names(sim.portPnL) <- "Port.PnL"
VaR01.Historical=quantile(-sim.portPnL$Port.PnL,0.99)
VaR01.Historical
VaR05.Historical=quantile(-sim.portPnL$Port.PnL,0.95)
VaR05.Historical
```

##Historical Excess Shortfall
```{r}
ES.PnL <-sim.portPnL$Port.PnL
ES.PnL$dummy01<-ifelse(ES.PnL$Port.PnL< (- VaR01.Historical) ,1,0)
ES.PnL$dummy05<-ifelse(ES.PnL$Port.PnL< (-VaR05.Historical) ,1,0)
shortfall01<-subset(ES.PnL,ES.PnL$dummy01==1)
shortfall05<-subset(ES.PnL,ES.PnL$dummy05==1)
ES01.Historical<- -mean(shortfall01$Port.PnL)
ES01.Historical
ES05.Historical<- -mean(shortfall05$Port.PnL)
ES05.Historical
```

##Stock Return Prediction
```{r}
alpha=0.02978
beta=4.32094
riskfree=1.15
riskfree.monthly<-(1+riskfree/100)^(3/12)-1
stockindexreturn<-mean((ST-S0)/S0)
marketReturn<-(ST-S0)/S0
stockReturnList=beta*(marketReturn-riskfree.monthly)+alpha+riskfree.monthly
stockReturn<-mean(stockReturnList)
stockRisk<-sd(stockReturnList)
stockReturn
stockRisk
```

##bond
```{r}
t3mo <- getSymbols('DGS3MO',src='FRED', auto.assign = FALSE)
t10yr <- getSymbols('DGS10',src='FRED', auto.assign = FALSE)

treasury<-t3mo
treasury<-merge(treasury,t10yr)
extreme<-subset(treasury, index(treasury) >= "2013-12-31" & index(treasury) <= "2017-10-31")
head(extreme)
extreme<-extreme/100
cor3mo10yr<-lm(formula=DGS10~DGS3MO,data=extreme)
longtermreturn<-extreme[nrow(extreme),]
sigma<-sd(extreme$DGS3MO,na.rm = TRUE)*sqrt(252)
BONDS0 = 0.0115
T = 0.25
riskfree = 0.0115
drift = (riskfree-0.5*sigma^2)
BONDST <- gbm.paths(w1[1:10000],BONDS0,drift,sigma,T)
head(BONDST)
summary(cor3mo10yr)
DGS103mo=-0.034484*BONDST+0.022151
bondprc<-function(coupon,maturity,yield,par,coupon.freq){
  periods=maturity*coupon.freq
  coupon.period=coupon/coupon.freq
  yield.period=yield/coupon.freq
  bond.coupon<-rep(coupon.period,times=periods,length.out=NA,each=1)
  bond.df<-as.data.frame(bond.coupon)
  for (i in 1:periods) {
    bond.df$cf[i]=par*coupon.period
    bond.df$period[i]=i
    bond.df$yield[i]=yield.period
    }
  bond.df$cf[periods]=bond.df$cf[periods]+par
  bond.df$PV=bond.df$cf/((1+bond.df$yield)^bond.df$period)
  value=sum(bond.df$PV)
  value
}
DGS103mo=data.frame(DGS103mo)
nrow(DGS103mo)

coupon=0.0238
maturity=10
par=1000
coupon.freq=2
yield<-rep(0,nrow(DGS103mo))
price<-rep(0,nrow(DGS103mo))
for(i in 1:nrow(DGS103mo)){
  yield[i]<-DGS103mo$DGS103mo[i]
  price[i]<-bondprc(coupon,maturity,yield[i],par,coupon.freq)
}
bondReturnList<-(price-par)/par
mean((price-par)/par)
sd((price-par)/par)
bondVaR01.Gaussian<- -(mean((price-par)/par)+sd((price-par)/par)*qnorm(0.01))*par
bondVaR01.Gaussian
bondVaR05.Gaussian<- -(mean((price-par)/par)+sd((price-par)/par)*qnorm(0.05))*par
bondVaR05.Gaussian
```
##option
```{r}
## sd of historical data
data.SOXL<-getSymbols("SOXL", from ="2013-12-31",to="2017-10-31",auto.assign = FALSE)
return.SOXL <- Return.calculate(data.SOXL$SOXL.Adjusted)
return.SOXL<-return.SOXL[-1,]
sd(return.SOXL)
##protective put
bs.opm <- function(S,K,T,riskfree,sigma,type){
  d1<-(log(S/K)+(riskfree+0.5*sigma^2)*T)/(sigma*sqrt(T))
  d2<-d1-sigma*sqrt(T)
  if(type=="Call"){
    opt.val<-S*pnorm(d1)-K*exp(-riskfree*T)*pnorm(d2)
  }
  if(type=="Put"){
    opt.val<-K*exp(-riskfree*T)*pnorm(-d2)-S*pnorm(-d1)
  }
  opt.val
}


S0 = 147.96	
Kcall = 1.05*S0
Kput = 0.95*S0
T = 0.25
riskfree = 0.0115  # 3-month US Treasury bill
sigma = sd(return.SOXL)*sqrt(252)
# Black-Scholes option pricing model for call and put
C0 <- bs.opm(S0,Kcall,T,riskfree,sigma,"Call")
P0 <- bs.opm(S0,Kput,T,riskfree,sigma,"Put")
c(C0,P0)


t = 0.25
drift = (riskfree-0.5*sigma^2) # using expected drift
St <- gbm.paths(w1[1:10000],S0,drift,sigma,t) # 10000 paths
paths <- data.frame(St)  # put data into a data frame
paths$call_moneyness <- ifelse(St-Kcall>0,St-Kcall,0)
paths$put_moneyness <- ifelse(Kput-St>0,Kput-St,0)

riskfree = 0.0115 # 3-month US Treasury bill, assumed to be unchanged from time 0
Tmt = 0.25         # only three months left on 6-month option

paths$Ct <- bs.opm(St,Kcall,Tmt,riskfree,sigma,"Call")
paths$Pt <- bs.opm(St,Kput,Tmt,riskfree,sigma,"Put")

paths$return_S <- 100*(paths$St-S0)/S0
paths$return_C <- 100*(paths$Ct-C0)/C0
paths$return_P <- 100*(paths$Pt-P0)/P0
optionCallList<-(paths$Ct-C0)/C0
mean((paths$Ct-C0)/C0)
sd((paths$Ct-C0)/C0)
optionPutList<-(paths$Pt-P0)/P0
mean((paths$Pt-P0)/P0)
sd((paths$Pt-P0)/P0)

```

##MV optimization for investment
```{r}
stockindexreturnList<-data.frame(stockindexreturnList)
stockReturnList<-data.frame(stockReturnList)
bondReturnList<-data.frame(bondReturnList)
optionCallList<-data.frame(optionCallList)
optionPutList<-data.frame(optionPutList)
investment.return<-cbind(stockindexreturnList,stockReturnList,bondReturnList,optionCallList,optionPutList)
nrow(optionCallList)
VCOV.MV <- cov(investment.return)

avg.ret<-rbind(0.003448167,0.03517252,0.01563858,0.5205084,0.5205084)
min.ret<-0.003448167
max.ret<-0.5205084

increments=100
tgt.ret<-seq(min.ret,max.ret,length=increments)
head(tgt.ret)
tgt.sd<-rep(0,length=increments)
wgt<-matrix(0,nrow=increments,ncol=length(avg.ret))
library(Matrix)
Dmat<-2*VCOV.MV
pd_D_mat <- nearPD(Dmat)
library(quadprog)
for (i  in 1:100){
 
  Dmat = as.matrix(pd_D_mat$mat)
  dvec<-c(rep(0,length(avg.ret)))
  Amat<-cbind(rep(1,length(avg.ret)),avg.ret,diag(1,nrow=5))
  bvec<-c(1,tgt.ret[i],rep(0,5))
  soln<-solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=0)
  tgt.sd[i]<-sqrt(soln$value)
  wgt[i,]<-soln$solution
}

colnames(wgt)<-paste(c("wgt.index", "wgt.stock", "wgt.bond", "wgt.call", "wgt.put"))
wgt[1,2]<-0
wgt[nrow(wgt),1]<-0

tgt.port<-data.frame(cbind(tgt.ret,tgt.sd,wgt))
minvar.port<-subset(tgt.port,tgt.port$tgt.sd==min(tgt.port$tgt.sd))
riskfree <- 0.0115
tgt.port$Sharpe<-(tgt.port$tgt.ret-riskfree)/tgt.port$tgt.sd
tangency.port<-subset(tgt.port,tgt.port$Sharpe==max(tgt.port$Sharpe))
eff.frontier<-subset(tgt.port,tgt.port$tgt.ret>=minvar.port$tgt.ret)

plot(x=tgt.sd, xlab="Portfolio Risk", y=tgt.ret, ylab="Portfolio Return", col="gray40",
main="Mean-Variance Efficient Frontier")
abline(h=0,lty=1)
points(x=minvar.port$tgt.sd,y=minvar.port$tgt.ret,pch=17,cex=3)
points(x=tangency.port$tgt.sd,y=tangency.port$tgt.ret,pch=19,cex=3)
points(x=eff.frontier$tgt.sd,y=eff.frontier$tgt.ret, col ="pink" )

finalVaR05.Gaussian<- -(0.28+0.1*qnorm(0.01))*50000
finalVaR05.Gaussian<- -(0.22+0.05*qnorm(0.01))*50000
bondVaR01.Gaussian
bondVaR05.Gaussian<- -(mean((price-par)/par)+sd((price-par)/par)*qnorm(0.05))*par
bondVaR05.Gaussian

```
